### 2013-02-16 doc/icml2013/algo.tex

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12moments,anandkumar12svd,AnandkumarHsuKakade2012}.
Our work extends this line of work into the space of discriminative models,
which requires regression to obtain the desired tensor.

>>>>

% Spectral
In recent years, there has a been substantial interest in ``spectral'' methods
for learning latent-variable models.  One line of work has
focused on observable operator models \cite{hsu09spectral}
in which the true parameters are not recovered, but a reparametrization is used
which enables prediction.
Another line of work is based on the method of moments and uses eigendecomposition of a certain tensor
to recover the parameters \cite{anandkumar12svd,anandkumar12moments,AnandkumarHsuKakade2012}.
Our work extends this line of work into the space of discriminative models,
which requires regression to obtain the desired tensor.

### 2013-02-16 doc/icml2013/evaluation.tex
Updated figures

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent
algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
The algorithm
was initialized with the regularized least squares solution and was run
for 500 iterations or until convergence up to a tolerance of $10^{-3}$. Both regularization parameters,
$\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$.

@@

\begin{figure*}[p]
  \centering
  \subfigure[Spectral]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{A comparison between Spectral Experts and EM. The dashed lines
  on the left denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to find
  the true global minima. The dotted lines on the right show different
  local optima found by EM on this example.}
  \label{fig:curves}
\end{figure*}

@@

\begin{table*}[p]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ ($n = 500,000$).}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

\begin{figure*}[p]
  \centering
  \subfigure[Well Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified Data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Recovery error vs $n$  ($b = 1, d = 5, k = 3, n = 500,000$).}
  \label{fig:vs-n}
\end{figure*}

@@

\begin{table*}[t]
\caption{Parameter Recovery Error $\|\theta^* - \hat \theta\|_F$ with misspecified data ($n = 500,000$).}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

>>>>

We implemented the low rank recovery optimization routines for $M_2$ and
$M_3$ using a proximal subgradient descent
algorithm.%\cite{candes11phaselift,tomioka2010estimation}. (Note sure about this citation and not required?)
The algorithm
was initialized with the regularized least squares solution and was run
for 500 iterations or until convergence up to a tolerance of $10^{-3}$.
%Both regularization parameters, $\lambda_n^{(2)}$ and, $\lambda_n^{(3)}$ were annealed as $\frac{1}{n}$.

@@

\begin{figure*}[p]
  \centering
  \subfigure[Spectral, Spectral+EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-specm.pdf}}
    \hspace{-2em}
  \subfigure[EM]{
    \includegraphics[width=0.50\textwidth]{figures/curves-vis/1-8-3-em.pdf}}
%  \subfigure[Spectral + EM]{
%    \includegraphics[width=0.34\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \caption{Visualization of the parameters estimated by Spectral Experts versus EM.
  (a) The dashed lines denote the solution recovered by Spectral Experts. While
  not a perfect fit, it provides an good initialization for EM to further improve the solution (solid lines).
  (b) The dotted lines show different local optima found by EM.}
  \label{fig:curves}
\end{figure*}

@@

\begin{table*}[p]
\caption{Parameter error $\|\theta^* - \hat \theta\|_F$ ($n = 500,000$)
as the number of variables $b$, number of features $d$ and the number of components $k$ increases.
While Spectral by itself does not produce good parameter estimates, Spectral+EM improves
over EM significantly.
}
\label{tbl:parameter-recovery}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}

@@

\begin{figure*}[p]
  \centering
  \subfigure[Well-specified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1833-decay.pdf}
  }
    \hspace{-2em}
  \subfigure[Misspecified data]{
    \includegraphics[width=0.50\textwidth]{figures/vs-n/1-8-3-3-rm.pdf}
  }
  \caption{Learning curves: parameter error as a function of the number of samples $n$ ($b = 1, d = 5, k = 3$).}
  \label{fig:vs-n}
\end{figure*}

@@

\begin{table*}[t]
\caption{Parameter rrror $\|\theta^* - \hat \theta\|_F$ when the data is misspecified ($n = 500,000$).
Spectral+EM degrades slightly, but still outperforms EM overall.
}
\label{tbl:parameter-recovery-mis}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
